---
title: "tips about rmarkdown"
author: "Neo Wang"
date: "2018年3月23日"
output: html_document
---

## 1.设置global options：不展示代码、消息和警告信息

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE)
```

## 2.添加r代码块code chuncks：快捷键**ctrl + alt + I**

r代码的一些设置：

- include = FALSE：不显示代码和代码的结果，但是可以被其他代码引用；

- echo = FALSE:不显示代码，但是显示代码结果；

- message = FALSE:不显示代码的相关消息；

- warning = FALSE:不显示代码的警告信息；

- fig.cap = "...":图片的说明文字；

## 3.添加行内代码inline code:用一对反引号括起来`r code`

**示例1：**

```{r echo=TRUE}
# colorfunc <- "heat.colors"
# colorfunc <- "terrain.colors"
# colorfunc <- "topo.colors"
colorfunc <- "rainbow"
```

demostration of the `r colorfunc` function

### `r colorfunc`

```{r fig.cap="the maunga whau volcano", echo=FALSE}
image(volcano, col = get(colorfunc)(200))
```

## 4.在代码块中执行其他语言

code chunck中可以执行除R之外的其他语言：

- python

- bash

- SQL

- Rcpp

- CSS

- JavaScript

```{bash}

```






When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
